Efficient and Scalable Bipartite Matching through Fast Beta Linkage (fabl)

### 2021-09-30 Prelim/prelim.tex
new speed graphics for el salvador

	\begin{frame}{What is Record Linkage?}
	\begin{enumerate}
		\item Record linkage is the task of identifying duplicate records over noisy datasets.

@@

		\item Far ranging applications in business, public health, and human rights
	\end{enumerate}
	\end{frame}

\begin{frame}{Record Linkage in Practice}
	\begin{columns}
		\begin{column}{0.48\textwidth}
			\includegraphics<1->[width = \textwidth, height = 1.2\textwidth ]{ted_article2.png}

		\end{column}
		\begin{column}{0.48\textwidth}
			\includegraphics<2->[width = \textwidth, height = 1.2\textwidth ]{dnc_header.png}
		\end{column}
	\end{columns}
\end{frame}

@@

	\begin{frame}{Linkage through Comparison Vectors}
		\includegraphics[width = \textwidth, height = .7\textwidth ]{fs_graphic.png}
	\end{frame}

@@

\section{Fast Beta Linkage}
\begin{frame}{Notation}
\begin{itemize}
	\item File A with records indexed $i \in \{1, \ldots, n_A\}$ and file B with records $j \in \{1, \ldots, n_B\}$. We use $F$ features for linkage, with $L_f$ possible levels of agreement on feature $f$.

@@

		\item Hashing plus SEI can reduce memory requirements by >99%
		\begin{itemize}
			\item Simulation of $20,000 \times 20,000$ linkage task with 4 fields. Naive approach requires 6.4GB of storage for all-to-all comparisons, hashing and SEI requires 90MB.
		\end{itemize}
	\end{itemize}
\end{frame}

\section{Results}

@@

>>>>

	\begin{frame}{What is Record Linkage?}
	\begin{itemize}
		\item Record linkage is the task of identifying duplicate records over noisy datasets.

@@

		\item Far ranging applications in business, public health, and human rights

		\item \textbf{Bipartite matching} is the specific goal of matching one record in one dataset to most one match in another dataset
	\end{itemize}
	\end{frame}

\begin{frame}{Record Linkage in Practice}
	\begin{columns}
		\begin{column}{0.48\textwidth}
			\includegraphics<1->[width = \textwidth, height = .9\textwidth ]{ted_article2.png}

		\end{column}
		\begin{column}{0.48\textwidth}
			\includegraphics<2->[width = \textwidth, height = .9\textwidth ]{dnc_header.png}
		\end{column}
	\end{columns}
\end{frame}

@@

	\begin{frame}{Linkage through Comparison Vectors}
		\includegraphics[width = \textwidth, height = .6\textwidth ]{fs_graphic.png}
	\end{frame}

@@

\section{Fast Beta Linkage}
\begin{frame}{Notation}
\begin{itemize}
	\item File A with records indexed $i \in \{1, \ldots, n_A\}$ and file B with records $j \in \{1, \ldots, n_B\}$, with $n_A \geq n_B$. We use $F$ features for linkage, with $L_f$ possible levels of agreement on feature $f$.

@@

		\item Hashing plus SEI can reduce memory requirements by $>99$.
		\begin{itemize}
			\item Simulation of $20,000 \times 20,000$ linkage task with 4 fields. Naive approach requires 6.4GB of storage for all-to-all comparisons, hashing and SEI requires 90MB.
		\end{itemize}
	\end{itemize}
\end{frame}

\section{Simulation Studies}

@@

\section{El Salvador Homicide Case Study}

\begin{frame}{El Salvador Case Study}
	\begin{itemize}
		\item El Salvadoran Civil War (1980-1991)
		\item Lists of casualties collected by multiple organizations
		\begin{itemize}
			\item Salvadoran Human Rights Commissions (CDHES), $n_A = 4420$
			\item El Rescate - Tutela Regal (ERTL), $n_B = 1323$
			\item Features include first name, last name, date and place of death
		\end{itemize}
		\item We aim to find duplicate records across files
		\begin{itemize}
			\item Particularly difficult because families are often killed together, and some children share names with parents
		\end{itemize}

	\end{itemize}
\end{frame}

\begin{frame}{Run Time}
		\begin{columns}
		\begin{column}{0.48\textwidth}
			\centering
			\includegraphics<1->[width = .6\textwidth, height = .6\textwidth ]{../notes/figures/el_salvador/time_table_big_P2.png}

		\end{column}
		\begin{column}{0.48\textwidth}
			\centering
			\includegraphics<2>[width = .6\textwidth, height = .6\textwidth ]{../notes/figures/el_salvador/time_table_small_P2.png}	
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}{Posterior Inference}
	\includegraphics[width = \textwidth, height = .6\textwidth ]{../notes/figures/el_salvador/m_posterior_smallP.png}
\end{frame}

\begin{frame}{Posterior Inference}
	\includegraphics[width = \textwidth, height = .6\textwidth ]{../notes/figures/el_salvador/DID_distribution_smallP_bayes.png}
\end{frame}

\begin{frame}{Violations of One-to-One Matching}
	\centering
	\includegraphics[width = .9\textwidth, height = .4\textwidth ]{../notes/figures/el_salvador/rosa_records.png}
\end{frame}

\begin{frame}{Violations of One-to-One Matching}
	\includegraphics[width = \textwidth, height = .6\textwidth ]{../notes/figures/el_salvador/bad_mixing.png}
\end{frame}

\section{Conclusion}
